background points - is more better?

### 2019-01-09 src/background_points_no_check.Rmd
Updated for new background data. All plots complete.

```{r}
testbk100001999 <- test_back_df[sample(nrow(test_back_df), 10000), ]  #where 10000 = number of rows to sample (large sample as per maxent)
testbk200001999 <- test_back_df[sample(nrow(test_back_df), 20000), ]  
testbk300001999 <- test_back_df[sample(nrow(test_back_df), 30000), ]  
testbk500001999 <- test_back_df[sample(nrow(test_back_df), 50000), ]  
testbk1000001999 <- test_back_df[sample(nrow(test_back_df), 100000), ]  
testbk1900001999 <- test_back_df[sample(nrow(test_back_df), 190000), ]  
```

@@

```{r}
ggplot(test10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_ssh_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_mlp_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

```{r}
ggplot(testbk100001999, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_ssh_back.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_chl_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_o2_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_o2_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/201406_allbackgroundpoints.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
print(Sys.time()-strt) #time it took to run
```
ok now create the first lot of random for 2014_06

```{r}
testbk100002014 <- test_back_df[sample(nrow(test_back_df), 10000), ]  #where 10000 = number of rows to sample (large sample as per maxent)
testbk200002014 <- test_back_df[sample(nrow(test_back_df), 20000), ]  
testbk300002014 <- test_back_df[sample(nrow(test_back_df), 30000), ]  
testbk500002014 <- test_back_df[sample(nrow(test_back_df), 50000), ]  
testbk1000002014 <- test_back_df[sample(nrow(test_back_df), 100000), ]  
testbk1900002014 <- test_back_df[sample(nrow(test_back_df), 190000), ]  
```

@@

```{r}
ggplot(testbk100002014, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_ssh.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_chl_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

>>>>

```{r}
testbk10000 <- test_back_df[sample(nrow(test_back_df), 10000), ]  #where 10000 = number of rows to sample (large sample as per maxent)
testbk20000 <- test_back_df[sample(nrow(test_back_df), 20000), ]  
testbk50000 <- test_back_df[sample(nrow(test_back_df), 50000), ]  
testbk100000 <- test_back_df[sample(nrow(test_back_df), 100000), ]  
testbk190000 <- test_back_df[sample(nrow(test_back_df), 190000), ]  
```

@@

```{r}
ggplot(testbk10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png, "../output/env/background_point_check/200710_ssh_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_mlp_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

```{r}
ggplot(testbk10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_ssh_back.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_chl_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_o2_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/199902_o2_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/201406_allbackgroundpoints.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
print(Sys.time()-strt) #time it took to run
```

ok now create the first lot of random for 2014_06

```{r}
testbk10000 <- test_back_df[sample(nrow(test_back_df), 10000), ]  #where 10000 = number of rows to sample (large sample as per maxent)
testbk20000 <- test_back_df[sample(nrow(test_back_df), 20000), ]  
testbk50000 <- test_back_df[sample(nrow(test_back_df), 50000), ]  
testbk100000 <- test_back_df[sample(nrow(test_back_df), 100000), ]  
testbk190000 <- test_back_df[sample(nrow(test_back_df), 190000), ]  
```

@@

```{r}
ggplot(testbk10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_ssh.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk20000 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk50000 , na.rm = TRUE, colour = "green") + geom_density(data=testbk100000 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_chl_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
